Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-28 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Updating...

When combining non-disjoint events, there is a further subtlety whose
resolution will give us the final general condition for IVPMs. For
general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

>>>>

When combining non-disjoint events, there is a further subtlety whose
resolution will give us the final general condition for IVPMs. For
general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Marinacci1999,Marinacci_2004,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.
